---
title: "China Demo"
author: "James"
date: "4/15/2020"
urlcolor: blue
link-citations: yes
citecolor: blue
linkcolor: blue
bibliography: references.bib
biblio-style: apalike-url
output:
  pdf_document:
    number_sections: true
    citation_package: natbib
---

# Approach 1: Use the low-level function epi_grid, epi_bayesian_krig

## Load the data

We first load the data and converge the data set into a format that our function can work with. This is done by using epi_converge, with parameters x, y, case, population, map.

```{r, warning=FALSE, label="loading_data"}
library(EpiVis)
covid19_china_province <- read.csv("provinces_test.csv")
china_covid <- epi_converge(x=covid19_china_province$longitudes, 
                            y=covid19_china_province$latitudes,
                            case=covid19_china_province$total_con,
                            population=covid19_china_province$populations,
                            map='china')
```

## Visualize the grid

We then proceed to form a grid at which we would interpolate (or estimate) the rate at.            

```{r, echo=FALSE, label="Figure 1"}
china_grid <- epi_grid(china_covid, 170) # Want 170 points in the rectangle
                                         #  but only part of them would be in
                                         #  the map of china.
plot(china_grid, xlab="Longitude", ylab="Latitude", pch=15)
```

## Estimate rates at the grid location

We take an MCMC approach to estimate rates at the new locations on the grid. To be precise, we would model the rate as a Gaussian Process with constant mean and spherical covariance.

      
It should be noted that the estimated rate is multipled by 10000 to avoid machine precision problems; as a result, the estimated rate is the rate per 10000 people.         

```{r, warning=FALSE, label = "Figure 2", echo=FALSE}
require(rstan)
options(mc.cores = parallel::detectCores())
#Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
rstan_options(auto_write = TRUE)

fit <- epi_bayesian_krig(china_covid, china_grid, mod='krig', chain=4, iter=400)
## This saves a "spatial_stan.Rda" file locally automatically, 
##   as it is a side effect by epi_bayesian_krig.

r <- extract(fit, pars="rate_pred")

rate_pred <- NULL

library(maps)
for (i in 1:ncol(r$rate_pred)){
  rate_pred[i] = mean(r$rate_pred[401:800,i])
}

grid_pred <- cbind(china_grid$x, china_grid$y, rate_pred)
grid_pred <- grid_pred[order(rate_pred),]


## Some color of choice
col=c(rep(heat.colors(4)[4], nrow(grid_pred)/4), 
      rep(heat.colors(4)[3], nrow(grid_pred)/4), 
      rep(heat.colors(4)[2], nrow(grid_pred)/4), 
      rep(heat.colors(4)[1], nrow(grid_pred)/4))

china_covid <- china_covid[order(china_covid$rate),]

col2=c(rep(heat.colors(4)[4],8), rep(heat.colors(4)[3],8), 
          rep(heat.colors(4)[2],8), rep(heat.colors(4)[1], 8))

map('world','china')
points(grid_pred[,1], grid_pred[,2], col=col, pch=15, cex=1.5)
title(main=expression('Rate of Disease per 10000 people'),  xlab="Longitude", ylab="Latitude")

map('world','china')
points(china_covid$x, china_covid$y, col=col2, pch=15, cex=1.5)
title(main=expression('Mock Data Collected'),  xlab="Longitude", ylab="Latitude")
```

# Approach 2: Use the high-level function epi_heatmap

```{r, warning=FALSE, label="Figure 3", echo=FALSE}
library(EpiVis)
covid19_china_province <- read.csv("provinces_test.csv")
china_covid <- epi_converge(x=covid19_china_province$longitudes, 
                            y=covid19_china_province$latitudes,
                            case=covid19_china_province$total_con,
                            population=covid19_china_province$populations,
                            map='china')
epi_heatmap(epi=china_covid, pts=170)
```

\appendix

# R Code

```{r, ref.lab="Figure 1", eval=FALSE}

```

```{r, ref.lab="Figure 2", eval=FALSE}

```

```{r, ref.lab="Figure 3", eval=FALSE}

```
